Model LF

### 2022-10-12 max_dp endogen stød.Rmd
Commit

```{r}
shock_prod_model_shock=shock_prod_model %>% window(start= c(2006,3))
```

@@

 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

@@

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

rw_ds_03 = Shock_3$simulation$rw_ds
kuld_03 = Shock_3$simulation$shock_kuld
inflation_03 = Shock_3$simulation$inflation

prod_03 = Shock_3$simulation$prod
```

@@

plot(ur_ds_03, col= "red"); lines(ur_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

@@

>>>>

```{r}
shock_prod_model_shock=shock_prod_model %>% window(start= c(2016,3))
```

@@

 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2016,3),  FREQ='Q')

@@

```{r}
plot(prod_bs3, col= "green"); lines(prod, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

@@

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2016,3),  FREQ='Q')

@@

rw_ds_03 = Shock_3$simulation$rw_ds
kuld_03 = Shock_3$simulation$shock_kuld
inflation_03 = Shock_3$simulation$inflation
lf_03 = Shock_3$simulation$lf
prod_03 = Shock_3$simulation$prod
```

@@

plot(ur_ds_03, col= "red"); lines(ur_ds_bs3, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

@@

```{r}
plot((ur_ds_03-ur_ds_bs3), col= "red")
```
